Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-08-20 figures.Rmd
added figure 6

  df_hbox_long <- df_hbox %>% pivot_longer(cols = 4:ncol(.), names_to = "variable", values_to = "value")

@@

>>>>

  df_hbox_long <- df_hbox %>% pivot_longer(cols = 7:ncol(.), names_to = "variable", values_to = "value")

@@

### Figure 6: Hemoglobin concentration trends in extravascular edema vs vascular engorgement

```{r fig6, fig.width = 12}

df_fig6 <- tibble(edema = rnorm(n = 90, mean = 20, sd = 20),
                  normal = rnorm(n = 90, mean = 70, sd = 20),
                  engorge = rnorm(n = 90, mean = 130, sd = 20)) %>% 
  pivot_longer(1:3, names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = c("edema", "normal", "engorge")))

df_fig6 %>% 
  ggplot(aes(x = variable, y = value)) +
  geom_point(shape = 1, size = 3, position = position_jitter(0.1)) +
  stat_summary(fun = "median", geom = "crossbar", size = 0.2, width = 0.5) +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())
